Proposal: Loose Grammar Inference for Lossy Compression

### 2012-10-18 proposal.tex
Slight revising of intro

The scope of our focus will be like that of \Sequitur: we will consider the
composite application of both grammar transformation and grammar compression to
an input.

>>>>

As with \Sequitur, the scope of our problem will encompass the full conversion
pathway of the input data---both the grammar transformation and the grammar
compression steps---and we will consider introducing lossiness at each point in
the process.
